### 2022-04-14 GB_Simulation_3Species.Rmd
Updates

#LOAD HABITAT PREVIOUSLY CREATED
#hab <- readRDS(file="hab_justYT.RDS") #finer resolution
hab <- readRDS(file="hab_justYT2.RDS") #courser resolution

@@

@@

@@

hab <- readRDS("hab_GB_3species.RDS")

@@

STILL NEED: REC PARAMS, K GROWTH PARAMS

Recr(model = "BH", params = list("a" = 1000, "b" = 450),
   B = max(Pop[["Start_pop"]][["spp1"]],na.rm=T), cv = 0)

profvis::profvis({
#decreasing population settings
Pop <- init_pop_Bens(sim_init = sim, Bio = c("spp1" = 3194, "spp2" = (13000+30000)/2, "spp3" = 150000*1.2), #CHANGE
                     hab = hab[["hab"]], start_cell = list("spp1" = c(46,112),"spp2" = c(30,134),"spp3" = c(24,91)),
                     lambda = c("spp1" = 0, "spp2" = 0, "spp3" = 0), #set at 0 first, change after initial population set
                     init_move_steps = 20,
                     rec_params = list("spp1" = c("model" = "BH", "a" = 2, "b" = 4, "cv" = 0),
                                       "spp2" = c("model" = "BH", "a" = 2, "b" = 4, "cv" = 0),
                                       "spp3" = c("model" = "BH", "a" = 2, "b" = 4, "cv" = 0)), #CHANGE
                     rec_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14),
                     spwn_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14  ), #CORRECT FOR YTF
                     M = c("spp1" = 0.25+0, "spp2" = 0.35+0, "spp3" = 0.2+.05), #CHANGE
                     K = c("spp1" = 0.3, "spp2" = 0.3, "spp3" = 0.3), #CHANGE
                     nz = nonzero_idx)

>>>>

#LOAD HABITAT PREVIOUSLY CREATED
#hab <- readRDS(file="hab_justYT.RDS") #finer resolution
#hab <- readRDS(file="hab_justYT2.RDS") #courser resolution

hab <- readRDS(file="hab_GB_3species.RDS") #courser resolution

@@

par(mar=c(1,1,1,1))
fields::image.plot(hab[["hab"]][["spp2"]])

par(mar=c(1,1,1,1))
fields::image.plot(hab[["hab"]][["spp3"]])

@@

par(mar=c(1,1,1,1))
fields::image.plot(hab[["spwn_hab"]][["spp2"]])

par(mar=c(1,1,1,1))
fields::image.plot(hab[["spwn_hab"]][["spp3"]])

@@

#hab <- readRDS("hab_GB_3species.RDS")

@@

#profvis::profvis({
#decreasing population settings
Pop <- init_pop_Bens(sim_init = sim, Bio = c("spp1" = 3194, "spp2" = (13000+30000)/2, "spp3" = 150000*1.2), #CHANGE
                     hab = hab[["hab"]], start_cell = list("spp1" = c(46,112),"spp2" = c(30,134),"spp3" = c(24,91)),
                     lambda = c("spp1" = 0, "spp2" = 0, "spp3" = 0), #set at 0 first, change after initial population set
                     init_move_steps = 20,
                     rec_params = list("spp1" = c("model" = "BH", "a" = 108582, "b" = 4301, "cv" = 0),
                                       "spp2" = c("model" = "BH", "a" = 25922 , "b" = 3491, "cv" = 0),
                                       "spp3" = c("model" = "BH", "a" = 157783, "b" = 40530, "cv" = 0)), #CHANGE
                     rec_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14),
                     spwn_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14  ), 
                     M = c("spp1" = 1.478+.358, "spp2" = 1.299+.511, "spp3" = 1.097+.7985), #NEED F
                     K = c("spp1" = 1.417, "spp2" = 1.801, "spp3" = 1.422), 
                     nz = nonzero_idx)
